sem

### 2022-12-09 scripts/workshop/sem.Rmd
trying to use gams

library(tidyverse)
library(magrittr)
library(piecewiseSEM)
library(nlme)
library(lmerTest)
library(dagitty)

@@

cc ~ mean water temp; size ~ mean water temp; prevalence ~ cc + size + mean water temp
```{r}
cc_temp <- glm(log10(cc) ~ MeanWaterTempPredC, data = comm_data)
size_temp <- glm(log10(size) ~ MeanWaterTempPredC, data = comm_data)
prev_cc <- glm(Prevalence ~ log10(cc) + MeanWaterTempPredC + log10(size), data = comm_data)

>>>>

library(tidyverse)
library(magrittr)
library(piecewiseSEM)
library(nlme)
library(lmerTest)
library(mgcv)
library(dagitty)

@@

cc ~ mean water temp; size ~ mean water temp; prevalence ~ cc + size + mean water temp
```{r}
cc_temp <- gam(log10(cc) ~ s(MeanWaterTempPredC), family = gaussian, data = comm_data)
size_temp <- gam(log10(size) ~ s(MeanWaterTempPredC), family = gaussian, data = comm_data)
prev_cc <- glm(Prevalence ~ log10(cc) + log10(size), data = comm_data)
